The problem and promise of scale in multilayer networks

### 2020-01-22 paper/manuscript.Rmd
knit rmd
quick describe landcover scale

---
title: The problem and promise of scale in multilayer networks
author: Alec L. Robitaille, Quinn M.R. Webber, Julie W. Turner, Eric Vander Wal
output: 
    word_document
    #github_document
---

@@

>>>>

---
title: The problem and promise of scale in multilayer networks
author: Alec L. Robitaille, Quinn M.R. Webber, Julie W. Turner, Eric Vander Wal
output: 
    #word_document
    github_document
---

@@

### Variables/sensitivity

1. landcover scale

Sample same landcover product at different scales. Landcover is the Fogo landcover product. Resampled using `grainchanger` from regular resolution (believe it's 30m), to 100m, 250m, 500m, 1000m, 2500m (tentative numbers). Resampling method was modal moving window. Water areas were masked before resampling. Landcover reclassified to open, forest and lichen.

```
open <- c(1, 6, 7, 9)
forest <- c(2, 3, 4, 5)
lichen <- 8
```

1. spatial threshold
1. number of observations
1. time window length
1. time window position

### Metrics
